Efficient and Adjustable Run-Time Monitoring Using Dataflow-Guided Filtering

### 2014-09-12 related.tex
Revised related work.

% Monitoring
Many monitoring schemes have been developed for various security, reliability,
debugging, and other capabilities. There exist monitoring schemes for uninitialized
memory check \cite{mondrian-asplos02}, array bounds check
\cite{hardbound-asplos08, clause-ase07}, and dynamic information flow
tracking \cite{dift-asplos04, raksha-isca07, loki-osdi08}.
Memtracker \cite{memtracker-hpca07} uses monitoring to check for various
memory-related bugs and errors.  Control flow verification techniques perform
monitoring to check that program execution follows expected control flows
\cite{schuette-comp87, impres-dac06,
kayaalp-isca12}.  Our monitoring architecture is designed to
be generally applicable to any of these instruction-grained monitoring schemes.
In particular, our proposed architecture may be especially useful for some of
these more complex schemes which also have higher overheads.  Similarly,
although many of these schemes showed low overheads in custom hardware, our
architecture can be used to reduce the overheads when applying these schemes on
a multi-core platform.

% Filtering
FADE \cite{fade-hpca14} presents a general filtering engine in order to reduce
the overheads of monitoring. It filters out redundant updates and null checks
by reading metadata values. We do not handle filtering redundant updates, but
we do filter out null checks as well as null (i.e., uninitialized)
propagations.  We are able to do this because the dataflow engine can also
propagate the null information.  In addition, our dataflow engine only
requires reading and writing 2-bit flags rather than the entire metadata.  As
we have shown, our dataflow engine also enables adjustable overheads without
false positives which is not a capability described by FADE.

>>>>

% Monitoring
Many monitoring schemes have been developed for various security, reliability,
debugging, and other capabilities. There exist monitoring schemes for uninitialized
memory check \cite{mondrian-asplos02}, array bounds check
\cite{hardbound-asplos08, clause-ase07}, and dynamic information flow
tracking \cite{dift-asplos04, raksha-isca07, loki-osdi08}.
Memtracker \cite{memtracker-hpca07} uses monitoring to check for various
memory-related bugs and errors.  Control flow verification techniques perform
monitoring to check that program execution follows expected control flows
\cite{schuette-comp87, impres-dac06,
kayaalp-isca12}.  Our monitoring architecture is designed to
be generally applicable to any of these instruction-grained monitoring schemes.
% In particular, our proposed architecture may be especially useful for some of
% these more complex schemes which also have higher overheads.  Similarly,
% although many of these schemes showed low overheads in custom hardware, our
% architecture can be used to reduce the overheads when applying these schemes on
% a multi-core platform.

% Filtering
FADE \cite{fade-hpca14} presents a general filtering engine in order to reduce
the overheads of monitoring. It filters out redundant updates and null checks
by reading metadata values. 
By extending our dataflow engine for partial monitoring, we are able to also
filter out null checks as well as null metadata propagations, but we do not
handle filtering redundant updates.
% We are able to do this because the dataflow engine can also
% propagate the null information.  
In contrast to FADE, our dataflow engine only
requires reading and writing 2-bit flags rather than the entire metadata. 
% As
% we have shown, our dataflow engine also enables adjustable overheads without
% false positives which is not a capability described by FADE.
